\documentclass[a4paper, 10pt]{article}
\title{~ Ayan Ruzdan, 2023, May 5th, 1.42am - 2.07am.}
\date{}
\usepackage{geometry}
\geometry{a4paper,
% left = 20mm,
% right=20mm,
top=20mm,
bottom=20mm,
heightrounded}
\begin{document}
\maketitle
The rain was now hitting harder than before, yet she refused to move, sitting still in front of the store, hoping that he would return. Cars passing by, their red lights reflecting along the shiny roads, the rain was strong enough to hide her tears but not heavy enough to wash away her sorrows. Suddenly, it felt like the rain stopped, or maybe there was someone, someone who would protect her from the cold rain. But that's what she thought.

Suddenly strong winds started to blow, scattering the rain drops, making it even harder to see. A silhouette of a man, barely visible, was standing across the store street. He slowly crossed the road, holding his umbrella tight against the strong winds. He came up to her and placed his umbrella over her head, the sound of the raindrops now echoing under the umbrella. The man had a very familiar face, a face of someone you can trust, a face with a warm smile, a face that feels like home. She did not care about anything at all, all she wanted was someone she could embrace, and she just hugged the man. She closed her eyes, still clinging onto him. A few moments of silence passed. But she wished that these moments, the sound of the rain over the umbrella, the sound of the cars passing by, the strong wind, everything would stay the same forever, and she, forever in his arms. But the man handed the umbrella in her arms and said "You were right. None of this is real."

And the rain suddenly stopped, the raindrops fell like pearls off a snatched necklace, the world suddenly turned white, first the sky, then the roads, even her fingers turning pale. A few moments passed, and then she realized she had to go to the church.

After all, it was her funeral.

They say that you relive all of your memories before dying, and maybe this is what was happening in my case. And maybe the man that she had trusted so much, was actually the person to put her in this state. Maybe the circle of life might make a full loop someday, but for now her role was complete. She saw her mother, her face pale and ashen. And her sister, no matter how much she hated each other, that day she saw how swollen her sister's eyes were. Her father still trying to process the fact that her beloved daughter was now a part of sunsets and raindrops.

She wasn't planning on becoming a ghost, or being reborn. But it still felt like she could go back and save herself. Everything felt a little hazy. Was she actually dead? She saw herself being lowered down in the ground. Oh what a weird feeling! But as she was being lowered down, she felt the rain falling much harder again. The winds blowing strong, scattering the raindrops, making it even harder to see. She suddenly had the urge to drink something warm. "Maybe some soup", she thought.

She felt her body moving on it's own, and found herself in a convenience store. She wandered around a bit and found a packet of soup. The store somehow reminded her of someone who used to be her sunshine, her beloved, her everything. But now the person was gone, and all there was left was a void. She paid for the soup and went outside the shop, the rain was even stronger now, there was no limit to how angry the gods could be that day, it felt like the entire city would be flooded. By this time her mind was in an entirely different emotional state, and she sat down in front
of the store, hoping that that certain someone would return.
\end{document}
